---
title: "Gender Difference and Onset Age"
author: "Pengyuan Yang"
date: "2023-03-11"
output: html_document
---



```{r}
library(readxl) 
library(writexl)
library(metafor)
library(ggplot2)
theme_set(theme_bw())
```

```{r}
GenderDiff <- read_xlsx("C:/Users/Lauren/Desktop/meta analysis/data analysis/input/gender difference-20240131.xlsx")

GenderDiff$First_Author <- sub(",.*", " et al.", GenderDiff$First_Author)
```

#---Gender difference preprocess---#
```{r}
GenderDiffNum <- subset(GenderDiff, is.na(GenderDiff[,32])==FALSE | is.na(GenderDiff[,33])==FALSE)
#GenderDiffNum <- GenderDiffNum[-c(24,25,26,28),] #One study included in OR
GenderDiffMS <- subset(GenderDiff, is.na(GenderDiff[,40])==FALSE | is.na(GenderDiff[,42])==FALSE)
GenderDiffOR <- subset(GenderDiff, is.na(GenderDiff[,48])==FALSE | is.na(GenderDiff[,51])==FALSE)

#preprocess Num data
id <- nrow(GenderDiffNum)

StudyInfo <- rbind(GenderDiffNum[,c(7:31)],GenderDiffNum[,c(7:31)])

GenderORNum <- as.data.frame(matrix(rep(NA,id*6),nrow = id*2, ncol = 3, byrow = TRUE))
GenderLogORNum <- as.data.frame(matrix(rep(NA,id*6),nrow = id*2, ncol = 3, byrow = TRUE))
colnames(GenderORNum) <- c("OR", "LCI", "UCI")
colnames(GenderLogORNum) <- c("OR", "LCI", "UCI")


i=1
j=32
while (i<=id) {
     if (is.na(GenderDiffNum[i,j])==FALSE){
        grp1yesM = as.numeric(GenderDiffNum[i,j])
        grp1noM = as.numeric(GenderDiffNum[i,j+2])
        grp2yesM = as.numeric(GenderDiffNum[i,j+4])
        grp2noM = as.numeric(GenderDiffNum[i,j+6])
        
     
        vM <- 1/grp1yesM + 1/grp1noM + 1/grp2yesM + 1/grp2noM
        esM <- (grp1yesM * grp2noM)/(grp1noM * grp2yesM)
        GenderORNum[i,1] <- esM
        GenderORNum[i,2] <- exp(log(esM)-1.96*sqrt(vM))
        GenderORNum[i,3] <- exp(log(esM)+1.96*sqrt(vM))
        GenderLogORNum[i,1] <- log(esM)
        GenderLogORNum[i,2] <- log(esM)-1.96*sqrt(vM)
        GenderLogORNum[i,3] <- log(esM)+1.96*sqrt(vM)
        
     }
     if (is.na(GenderDiffNum[i,j+1])==FALSE){
        grp1yesF = as.numeric(GenderDiffNum[i,j+1])
        grp1noF = as.numeric(GenderDiffNum[i,j+3])
        grp2yesF = as.numeric(GenderDiffNum[i,j+5])
        grp2noF = as.numeric(GenderDiffNum[i,j+7])
        
     
        vF <- 1/grp1yesF + 1/grp1noF + 1/grp2yesF + 1/grp2noF
        esF <- (grp1yesF * grp2noF)/(grp1noF * grp2yesF)
        GenderORNum[i+id,1] <- esF
        GenderORNum[i+id,2] <- exp(log(esF)-1.96*sqrt(vF))
        GenderORNum[i+id,3] <- exp(log(esF)+1.96*sqrt(vF))
        GenderLogORNum[i+id,1] <- log(esF)
        GenderLogORNum[i+id,2] <- log(esF)-1.96*sqrt(vF)
        GenderLogORNum[i+id,3] <- log(esF)+1.96*sqrt(vF)
        
      }

      i=i+1
}

GenderORNum <- cbind(StudyInfo, GenderORNum)
GenderORNum$Gender <- gl(2,id, labels = c("Male", "Female"))
GenderLogORNum <- cbind(StudyInfo, GenderLogORNum)
GenderLogORNum$Gender <- gl(2,id, labels = c("Male", "Female"))

#preprocess MS data
id <- nrow(GenderDiffMS)

StudyInfo <- rbind(GenderDiffMS[,c(7:31)], GenderDiffMS[,c(7:31)])

GenderORMS <- as.data.frame(matrix(rep(NA,id*6),nrow = id*2, ncol = 3, byrow = TRUE))
GenderLogORMS <- as.data.frame(matrix(rep(NA,id*6),nrow = id*2, ncol = 3, byrow = TRUE))
colnames(GenderORMS) <- c("OR", "LCI", "UCI")
colnames(GenderLogORMS) <- c("OR", "LCI", "UCI")

i=1
j=40  # it should be 40, the column starting with the mean/sd data
while (i<=id) {
      grp1mM = as.numeric(GenderDiffMS[i,j])
      grp1sdM = as.numeric(GenderDiffMS[i,j+1])
      grp1mF = as.numeric(GenderDiffMS[i,j+2])
      grp1sdF = as.numeric(GenderDiffMS[i,j+3])
      
      grp2mM = as.numeric(GenderDiffMS[i,j+4])
      grp2sdM = as.numeric(GenderDiffMS[i,j+5])
      grp2mF = as.numeric(GenderDiffMS[i,j+6])
      grp2sdF = as.numeric(GenderDiffMS[i,j+7])
      
      grp1nM = as.numeric(GenderDiffMS[i,28])  # I changed the column of sample size for the 4 groups
      grp1nF = as.numeric(GenderDiffMS[i,29])
      grp2nM = as.numeric(GenderDiffMS[i,30])
      grp2nF = as.numeric(GenderDiffMS[i,31])
      # Here i need to check carefully if it is correct.
      pooledSDM <- sqrt(((grp1nM-1)*grp1sdM^2+(grp2nM-1)*grp2sdM^2)/(grp1nM+grp2nM-2))
      pooledSDF <- sqrt(((grp1nF-1)*grp1sdF^2+(grp2nF-1)*grp2sdF^2)/(grp1nF+grp2nF-2))
      
      esM <- (grp1mM-grp2mM)/pooledSDM
      esF <- (grp1mF-grp2mF)/pooledSDF
      
      SEM <- sqrt((grp1nM+grp2nM)/(grp1nM*grp2nM)+esM^2/(2*(grp1nM+grp2nM)))
      SEF <- sqrt((grp1nF+grp2nF)/(grp1nF*grp2nF)+esF^2/(2*(grp1nF+grp2nF)))
      
      GenderORMS[i,1] <- exp(esM*pi/sqrt(3))
      GenderORMS[i,2] <- exp((esM-1.96*SEM)*pi/sqrt(3))
      GenderORMS[i,3] <- exp((esM+1.96*SEM)*pi/sqrt(3))
      
      GenderORMS[i+id,1] <- exp(esF*pi/sqrt(3))
      GenderORMS[i+id,2] <- exp((esF-1.96*SEF)*pi/sqrt(3))
      GenderORMS[i+id,3] <- exp((esF+1.96*SEF)*pi/sqrt(3))
      
      GenderLogORMS[i,1] <- esM*pi/sqrt(3)
      GenderLogORMS[i,2] <- (esM-1.96*SEM)*pi/sqrt(3)
      GenderLogORMS[i,3] <- (esM+1.96*SEM)*pi/sqrt(3)
      
      GenderLogORMS[i+id,1] <- esF*pi/sqrt(3)
      GenderLogORMS[i+id,2] <- (esF-1.96*SEF)*pi/sqrt(3)
      GenderLogORMS[i+id,3] <- (esF+1.96*SEF)*pi/sqrt(3)

      i=i+1
}

GenderORMS <- cbind(StudyInfo, GenderORMS)
GenderORMS$Gender <- gl(2,id, labels = c("Male", "Female"))
GenderLogORMS <- cbind(StudyInfo, GenderLogORMS)
GenderLogORMS$Gender <- gl(2,id, labels = c("Male", "Female"))

#preprocess OR data
GenderDiffOR <- GenderDiffOR[,-c(1:6, 32:47)]
id <- nrow(GenderDiffOR)
StudyInfo <- rbind(GenderDiffOR[,1:25], GenderDiffOR[,1:25])

OR <- as.data.frame(matrix(rep(NA,id*6),nrow = id*2, ncol = 3, byrow = TRUE))
colnames(OR) <- c("OR", "LCI", "UCI")
OR[c(1:id),] <- GenderDiffOR[,c(26:28)]
OR[c((id+1):(id*2)),] <- GenderDiffOR[,c(29:31)]
OR <- apply(OR, 2, as.numeric)
logOR <- log(OR)

GenderDiffOR <- cbind(StudyInfo, OR)
GenderDiffOR$Gender <- gl(2,id, labels = c("Male", "Female"))
GenderDiffLogOR <- cbind(StudyInfo, logOR)
GenderDiffLogOR$Gender <- gl(2,id, labels = c("Male", "Female"))

#integrate
GenderORData <- rbind(GenderORNum, GenderORMS, GenderDiffOR)
GenderORData <- GenderORData[complete.cases(GenderORData$OR),]
GenderLogORData <- rbind(GenderLogORNum, GenderLogORMS, GenderDiffLogOR)
GenderLogORData <- GenderLogORData[complete.cases(GenderLogORData$OR),]


# exclude duplicates
GenderORData <- subset(GenderORData, GenderORData$First_Author!= "Furukawa (adjusted) et al.")
GenderORData <- subset(GenderORData, GenderORData$First_Author!= "Mansueto (adjusted) et al.")
# excluded ones without female and male sample size
GenderORData <- subset(GenderORData, GenderORData$First_Author!= "McGrath et al.") 
GenderORData <- subset(GenderORData,GenderORData$First_Author!= "Hoffmann et al.")
GenderORData <- subset(GenderORData, GenderORData$First_Author!= "Barry et al.")

GenderLogORData <- subset(GenderLogORData, GenderLogORData$First_Author!= "Furukawa (adjusted) et al.")
GenderLogORData <- subset(GenderLogORData, GenderLogORData$First_Author!= "Mansueto (adjusted) et al.")
# excluded ones without female and male sample size
GenderLogORData <- subset(GenderLogORData, GenderLogORData$First_Author!= "McGrath et al.") 
GenderLogORData <- subset(GenderLogORData,GenderLogORData$First_Author!= "Hoffmann et al.")
GenderLogORData <- subset(GenderLogORData, GenderLogORData$First_Author!= "Barry et al.")


#save
write_xlsx(GenderORData,"C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/GenderOR.xlsx")
write_xlsx(GenderLogORData,"C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/GenderLogOR.xlsx")

```
#---prepare data---
```{r}
GenderData <- read_xlsx("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/GenderLogOR.xlsx")


#GenderData <- subset(GenderData, GenderData$First_Author!= "Millman et al.") #Exclude outliers
#GenderData <- subset(GenderData, GenderData$First_Author!= "Gayer-Anderson (SA)") 


GenderData <- subset(GenderData, is.na(GenderData$OR)==FALSE)
GenderData$se <- (GenderData$UCI-GenderData$LCI)/(1.96*2)
colnames(GenderData)[1:2] <- c("Author", "Year")
write_xlsx(GenderData, "C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/GenderData.xlsx")
```


#3.3---Forest plot---#
```{r}
GenderData <- read_excel("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/subgroup/GenderLogOR_main.xlsx")
GenderData <- subset(GenderData, GenderData$Author!= "Millman et al.") #Exclude outliers
#get the number of male and female ORs
maleNum <- nrow(subset(GenderData, GenderData$Gender=="Male"))
femaleNum <- nrow(subset(GenderData, GenderData$Gender=="Female"))
Male <- subset(GenderData, Gender=="Male")
Female <- subset(GenderData, Gender=="Female")
GenderData <- rbind(Male[order(Male$Year, Male$Author, decreasing = T),],
                    Female[order(Female$Year, Female$Author, decreasing = T),])
GenderData$Gender <- factor(GenderData$Gender, levels = c("Male", "Female"))
GenderData$Sample <- ifelse(GenderData$Gender=="Female",GenderData$N_Total_Female,GenderData$N_Total_Male)

# fit random-effects model
res <- rma(yi=OR, sei=se, data=GenderData, slab=paste(Author, Year, sep=", "))

# a little helper function to add Q-test, I^2, and tau^2 estimate info
mlabfun <- function(text, res) {
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=2, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(res$I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")")))}

### set up forest plot (with 2x2 table counts added; the 'rows' argument is
### used to specify in which rows the outcomes will be plotted)
jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/Genderplot_excluding0317.jpg", width =3000, heigh = 4500, res=500)
forest(res, at=log(c(0.05, 0.25, 1, 5, 25, 80)), atransf=exp, ilab=cbind(Sample), ilab.xpos=-4, xlim=c(-11,8), level=95,
       cex=0.75, ylim=c(-1, maleNum+femaleNum+10), 
       order= Gender, 
       rows=c(3:(maleNum+2), (maleNum+7):(maleNum+femaleNum+6)), 
       header=c("Author, Year","Odds Ratio [95% CI]"), xlab="Odds Ratio (Log Scale)",addfit = FALSE)

abline(h = 0, lty = 1, col = "black", lwd = 1)
### set font expansion factor (as in forest() above) and use a bold font
op <- par(cex=0.75, font=2)
text(-4,maleNum+femaleNum+9, c("Sample Size"))
 
### switch to bold italic font
par(font=4)
 
### add text for the subgroups
text(-11, c(maleNum+femaleNum+7,maleNum+3), pos=4, 
     c("Female", "Male"))
 
### set par back to the original settings
par(op)
 
### fit random-effects model in the three subgroups
res.male <- rma(yi=OR, sei=se, subset=(Gender=="Male"), data=GenderData)
res.female <- rma(yi=OR, sei=se, subset=(Gender=="Female"), data=GenderData)
 
### add summary polygons for the three subgroups
addpoly(res.female, row=maleNum+5.5, mlab=mlabfun("RE Model for subgroup", res.female))
addpoly(res.male, row= 1.5, mlab=mlabfun("RE Model for subgroup", res.male))
 
### fit meta-regression model to test for subgroup differences
res.meta <- rma(yi=OR, sei=se, mods = ~ Gender, data=GenderData)
summary(res.meta)
 
### add text for the test of subgroup differences
text(-11, -2, pos=4, cex=0.75, bquote(paste("Test for Subgroup Differences: ",
     Q[M], " = ", .(formatC(res.meta$QM, digits=2, format="f")), ", df = ", .(res.meta$p - 1),
     ", p = ", .(formatC(res.meta$QMp, digits=2, format="f")))),font = 2)

dev.off

```
#--pdf for gender differences---
```{r}
pdf("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/Genderplot_excluding0317.pdf", width = 10, heigh = 15)
forest(res, at=log(c(0.05, 0.25, 1, 5, 25, 80)), atransf=exp, ilab=cbind(Sample), ilab.xpos=-4, xlim=c(-11,8), level=95,
       cex=0.75, ylim=c(-1, maleNum+femaleNum+10), 
       order= Gender, 
       rows=c(3:(maleNum+2), (maleNum+7):(maleNum+femaleNum+6)), 
       header=c("Author, Year","Odds Ratio [95% CI]"), xlab="Odds Ratio (Log scale)",addfit = FALSE)

abline(h = 0, lty = 1, col = "black", lwd = 1)
### set font expansion factor (as in forest() above) and use a bold font
op <- par(cex=0.75, font=2)
text(-4,maleNum+femaleNum+9, c("Sample Size"))
 
### switch to bold italic font
par(font=4)
 
### add text for the subgroups
text(-11, c(maleNum+femaleNum+7,maleNum+3), pos=4, 
     c("Female", "Male"))
 
### set par back to the original settings
par(op)
 
### fit random-effects model in the three subgroups
res.male <- rma(yi=OR, sei=se, subset=(Gender=="Male"), data=GenderData)
res.female <- rma(yi=OR, sei=se, subset=(Gender=="Female"), data=GenderData)
 
### add summary polygons for the three subgroups
addpoly(res.female, row=maleNum+5.5, mlab=mlabfun("RE Model for subgroup", res.female))
addpoly(res.male, row= 1.5, mlab=mlabfun("RE Model for subgroup", res.male))
 
### fit meta-regression model to test for subgroup differences
res.meta <- rma(yi=OR, sei=se, mods = ~ Gender, data=GenderData)
summary(res.meta)
 
### add text for the test of subgroup differences
text(-11, -2, pos=4, cex=0.75, bquote(paste("Test for Subgroup Differences: ",
     Q[M], " = ", .(formatC(res.meta$QM, digits=2, format="f")), ", df = ", .(res.meta$p - 1),
     ", p = ", .(formatC(res.meta$QMp, digits=2, format="f")))),font = 2)

dev.off
```
#--- leave 1 out analysis
```{r}
df_male <- leave1out(res.male)
min_row <- df_male[df_male$estimate == min(df_male$estimate), ]
min_ci_lb <- exp(min_row$ci.lb)
min_ci_ub <- exp(min_row$ci.ub)
cat("The minium of OR for male is",exp(min(df_male$estimate)),":", min_ci_lb, "-", min_ci_ub)

max_row <- df_male[df_male$estimate == max(df_male$estimate), ]
max_ci_lb <- exp(max_row$ci.lb)
max_ci_ub <- exp(max_row$ci.ub)
cat("The maximum of OR for male  is",max(exp(df_male$estimate)),":", max_ci_lb, "-", max_ci_ub)

df_female <- leave1out(res.female)
min_row <- df_female[df_female$estimate == min(df_female$estimate), ]
min_ci_lb <- exp(min_row$ci.lb)
min_ci_ub <- exp(min_row$ci.ub)
cat("The minium of OR for female  is",exp(min(df_female$estimate)),":", min_ci_lb, "-", min_ci_ub)

max_row <- df_female[df_female$estimate == max(df_female$estimate), ]
max_ci_lb <- exp(max_row$ci.lb)
max_ci_ub <- exp(max_row$ci.ub)
cat("The maximum of OR for female  is",exp(max(df_female$estimate)),":", max_ci_lb, "-", max_ci_ub)
```




Basic information
```{r}
# Assuming "Gender" is a column in GenderData
num_male_rows <- nrow(subset(GenderData, Gender == "Male"))
num_female_rows <- nrow(subset(GenderData, Gender == "Female"))

# Print the results
cat("Number of rows for Male:", num_male_rows, "\n")
cat("Number of rows for Female:", num_female_rows, "\n")

cat("The total males of gender analysis is:",sum(GenderData[,"N_Total_Male"]), "\n")
cat("The total females of gender analysis is:",sum(GenderData[,"N_Total_Female"]), "\n")
cat("The total sample size of patients analysis in gender analysis is:",sum(GenderData$N_PT,na.rm = TRUE), "\n")
cat("The total sample size of Cases analysis in gender analysis is:",sum(GenderData$N_HC,na.rm = TRUE), "\n")


```

#---publication bias
```{r}
# egger test and fail safe N
egger_test_male <- regtest(res.male)
egger_test_male

egger_test_female <- regtest(res.female)
egger_test_female

GenderData_male <-  subset(GenderData,GenderData$Gender =="Male")

fsn(res.male,sei = se, data=GenderData, type = "Orwin", target = 0.1)

GenderData_female <-  subset(GenderData,GenderData$Gender =="Female")

fsn(res.female,sei = se, data=GenderData_female, type = "Orwin", target = 0.1)


jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/data analysis/output/Gender difference/publication bias/female_male_overall.jpg", width = 3000, height = 4000, res = 350)

# Define the layout with two rows and one column
par(mfrow = c(2, 1))

# Plot the funnel plot for the threat dimension
metafor::funnel(res.female, main = "Funnel Plot for the Overall Adversity in Woman")

# Plot the funnel plot for the deprivation dimension
metafor::funnel(res.male, main = "Funnel Plot for the Overall Adversity in Men ")

# Close the jpeg device
dev.off()
```




#3.4 Data only with CT
```{r}
Gender_MR <- read_xlsx("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/subgroup/GenderLogOR_main.xlsx")

# excluded ones without female and male sample size
Gender_CT <- subset(Gender_MR, Gender_MR$Author!= "Millman et al.") #Exclude outliers
Gender_CT <-  subset(Gender_MR, Gender_MR$`with CT`!= "N")

res.meta_sex_CT <- rma(yi=OR, sei=se, mods = ~ Gender, data=Gender_CT)
summary(res.meta_sex_CT)

GenderData <- Gender_CT
#------forest plot-----
maleNum <- nrow(subset(GenderData, GenderData$Gender=="Male"))
femaleNum <- nrow(subset(GenderData, GenderData$Gender=="Female"))

# fit random-effects model
res <- rma(yi=OR, sei=se, data=GenderData, slab=paste(Author, Year, sep=", "))

# a little helper function to add Q-test, I^2, and tau^2 estimate info
mlabfun <- function(text, res) {
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=2, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(res$I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")")))}

### used to specify in which rows the outcomes will be plotted)
jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/Genderplot_CT.jpg", width =3000, heigh = 4500, res=300)
forest(res, at=log(c(0.05, 0.25, 1, 5, 25, 80)), atransf=exp, xlim=c(-11,8), level=95,
       cex=0.75, ylim=c(-1, maleNum+femaleNum+10), 
       order=Gender, 
       rows=c(3:(maleNum+2), (maleNum+7):(maleNum+femaleNum+6)), 
       header=c("Author,Year","Odds Ratio [95% CI]"), xlab="Odds Ratio (Log scale)", mlab=mlabfun("RE Model for All Studies", res))
 
### set font expansion factor (as in forest() above) and use a bold font
op <- par(cex=0.75, font=2)
#text(c(-5.5, -3.5),     csNum+cohortNum+ccNum+13, c("Country", "Sample Size"))
 
### switch to bold italic font
par(font=4)
 
### add text for the subgroups
text(-11, c(maleNum+femaleNum+7,maleNum+3), pos=4, 
     c("Female", "Male"))
 
### set par back to the original settings
par(op)
 
### fit random-effects model in the three subgroups
res.male <- rma(yi=OR, sei=se, subset=(Gender=="Male"), data=GenderData)
res.female <- rma(yi=OR, sei=se, subset=(Gender=="Female"), data=GenderData)
 
### add summary polygons for the three subgroups
addpoly(res.female, row=maleNum+5.5, mlab=mlabfun("RE Model for subgroup", res.female))
addpoly(res.male, row= 1.5, mlab=mlabfun("RE Model for subgroup", res.male))
 
### fit meta-regression model to test for subgroup differences
res.meta <- rma(yi=OR, sei=se, mods = ~ Gender, data=GenderData)
summary(res.meta)
 
### add text for the test of subgroup differences
text(-11, -2.5, pos=4, cex=0.7, bquote(paste("Test for Subgroup Differences: ",
     Q[M], " = ", .(formatC(res.meta$QM, digits=2, format="f")), ", df = ", .(res.meta$p - 1),
     ", p = ", .(formatC(res.meta$QMp, digits=2, format="f")))))

dev.off

```

#3.5--sexual abuse and forest plot
```{r}
Gender_SA <- read.csv("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/subgroup/GenderLogOR_SA.csv")
Gender_SA <- subset(Gender_SA, Gender_SA$Author!= "Millman et al.") #Exclude outliers


res.meta_sex_SA <- rma(yi=OR, sei=se, mods = ~ Gender, data=Gender_SA)
summary(res.meta_sex_SA)

res.meta_sex_SA2 <- rma(yi=OR, sei=se, mods = ~ Gender + Sample.Size_included, data=Gender_SA)
summary(res.meta_sex_SA2)

#-----------forest plot
GenderData <- Gender_SA

Male <- subset(GenderData, Gender=="Male")
Female <- subset(GenderData, Gender=="Female")
GenderData <- rbind(Male[order(Male$Year, Male$Author, decreasing = T),],
                    Female[order(Female$Year, Female$Author, decreasing = T),])
GenderData$Gender <- factor(GenderData$Gender, levels = c("Male", "Female"))
# Create a separate data frame for the forest plot

GenderData$AuthorYear = paste(GenderData$Author, GenderData$Year, sep = ", ")

#get the number of male and female ORs
maleNum <- nrow(subset(GenderData, GenderData$Gender=="Male"))
femaleNum <- nrow(subset(GenderData, GenderData$Gender=="Female"))
GenderData$Sample <- ifelse(GenderData$Gender=="Female",GenderData$N_Total_Female,GenderData$N_Total_Male)

# fit random-effects model
res <- rma(yi=OR, sei=se, data=GenderData, slab = paste(Author, Year, sep=", "))

### fit random-effects model in the three subgroups
res.male <- rma(yi=OR, sei=se, data=GenderData[GenderData$Gender == "Male", ])
res.male
res.female <- rma(yi=OR, sei=se, data=GenderData[GenderData$Gender == "Female", ])
res.female
res.male$data  <- res.male$data[order(res.male$data$Year, res.male$data$Author), ]
res.female$data<- res.male$data[order(res.male$data$Year, res.male$data$Author), ]

compute_prediction_interval <- function(res, df, alpha = 0.05) {
  lower_bound <- exp(res$b - qt(p = alpha / 2, df = df-1, lower.tail = FALSE) * sqrt((res$se)^2 + res$tau2))
  upper_bound <- exp(res$b + qt(p = alpha / 2, df = df-1, lower.tail = FALSE) * sqrt((res$se)^2 + res$tau2))
  return(c(lower_bound, upper_bound))
}


# Case-control study
pred_interval_male <- compute_prediction_interval(res.female, df = 9)
# Cross-sectional study
pred_interval_female <- compute_prediction_interval(res.male, df = 5)  
# Cohort study


result_prediction_interval <- data.frame(
  Study_Type = c("SA for male","SA for female"),
  Lower_Bound = c(pred_interval_male[1], pred_interval_female[1]),
  Upper_Bound = c(pred_interval_male[2],pred_interval_female[2])
)

result_prediction_interval

```
#---forest plot for SA
```{r}
# a little helper function to add Q-test, I^2, and tau^2 estimate info
mlabfun <- function(text, res) {
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=2, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(res$I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")")))}

### set up forest plot (with 2x2 table counts added; the 'rows' argument is
### used to specify in which rows the outcomes will be plotted)
jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/Genderplot_SA.jpg", width =3000, heigh = 2600, res=350)
forest(res, at=log(c(0.05, 0.25, 1, 5, 25, 80)), atransf=exp, xlim=c(-11,8), level=95,ilab=cbind(Sample), ilab.xpos=-4,
       cex=0.70, ylim=c(-1, maleNum+femaleNum+10), 
       order= Gender,
       rows=c(3:(maleNum+2), (maleNum+7):(maleNum+femaleNum+6)), 
       header=c("Author,Year","Odds Ratio [95% CI]"), xlab="Odds Ratio (Log scale)", addfit = FALSE)

abline(h = 0, lty = 1, col = "black", lwd = 1) 
### set font expansion factor (as in forest() above) and use a bold font
op <- par(cex=0.75, font=2)
text(-4, maleNum+femaleNum+9, c("Sample Size"))
 
### switch to bold italic font
par(font=4)
 
### add text for the subgroups
text(-11, c(maleNum+femaleNum+7,maleNum+3), pos=4, 
     c("Female", "Male"))
 
### set par back to the original settings
par(op)
 

### add summary polygons for the three subgroups
addpoly(res.female, row=maleNum+5.5, mlab=mlabfun("RE Model for subgroup", res.female))
addpoly(res.male, row= 1.5, mlab=mlabfun("RE Model for subgroup", res.male))
 
### fit meta-regression model to test for subgroup differences
res.meta <- rma(yi=OR, sei=se, mods = ~ Gender, data=GenderData)
summary(res.meta)
 
### add text for the test of subgroup differences
# Calculate the position below the last row

# Add text for the test of subgroup differences
text(x = -11, y =-1, pos = 4, cex = 0.70, 
     bquote(paste("Test for Subgroup Differences: ",
                   Q[M], " = ", .(formatC(res.meta$QM, digits = 2, format = "f")), 
                   ", df = ", .(res.meta$p - 1),
                   ", p = ", .(formatC(res.meta$QMp, digits = 2, format = "f")))))


dev.off

```

# leave 1 out analyses
```{r}
df_male <- leave1out(res.male)
min_row <- df_male[df_male$estimate == min(df_male$estimate), ]
min_ci_lb <- exp(min_row$ci.lb)
min_ci_ub <- exp(min_row$ci.ub)
cat("The minium of OR for male is",exp(min(df_male$estimate)),":", min_ci_lb, "-", min_ci_ub)

max_row <- df_male[df_male$estimate == max(df_male$estimate), ]
max_ci_lb <- exp(max_row$ci.lb)
max_ci_ub <- exp(max_row$ci.ub)
cat("The maximum of OR for male  is",max(exp(df_male$estimate)),":", max_ci_lb, "-", max_ci_ub)

df_female <- leave1out(res.female)
min_row <- df_female[df_female$estimate == min(df_female$estimate), ]
min_ci_lb <- exp(min_row$ci.lb)
min_ci_ub <- exp(min_row$ci.ub)
cat("The minium of OR for female  is",exp(min(df_female$estimate)),":", min_ci_lb, "-", min_ci_ub)

max_row <- df_female[df_female$estimate == max(df_female$estimate), ]
max_ci_lb <- exp(max_row$ci.lb)
max_ci_ub <- exp(max_row$ci.ub)
cat("The maximum of OR for female  is",exp(max(df_female$estimate)),":", max_ci_lb, "-", max_ci_ub)

```




# funel plots in SA
```{r}
egger_test_male <- regtest(res.male)
egger_test_male

egger_test_female <- regtest(res.female)
egger_test_female

GenderData_male <-  subset(GenderData,GenderData$Gender =="Male")

fsn(res.male,sei = se, data=GenderData, type = "Orwin", target = 0.1)

GenderData_female <-  subset(GenderData,GenderData$Gender =="Female")

fsn(res.female,sei = se, data=GenderData_female, type = "Orwin", target = 0.1)


jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/data analysis/output/Gender difference/publication bias/female_male_SA.jpg", width = 3000, height = 4000, res = 350)

# Define the layout with two rows and one column
par(mfrow = c(2, 1))

# Plot the funnel plot for the threat dimension
metafor::funnel(res.female, main = "Funnel Plot for SA in Woman")

# Plot the funnel plot for the deprivation dimension
metafor::funnel(res.male, main = "Funnel Plot for SA in Men ")

# Close the jpeg device
dev.off()

```




#3.6--Physical abuse and forest plot
```{r}
Gender_PA <- read.csv("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/subgroup/GenderLogOR_PA.csv")
Gender_PA <- subset(Gender_PA, Gender_PA$Author!= "Millman et al.") #Exclude outliers


res.meta_sex_PA <- rma(yi=OR, sei=se, mods = ~ Gender, data=Gender_PA)
summary(res.meta_sex_PA)
GenderData <- Gender_PA

Male <- subset(GenderData, Gender=="Male")
Female <- subset(GenderData, Gender=="Female")
GenderData <- rbind(Male[order(Male$Year, Male$Author, decreasing = T),],
                    Female[order(Female$Year, Female$Author, decreasing = T),])
GenderData$Gender <- factor(GenderData$Gender, levels = c("Male", "Female"))
# Create a separate data frame for the forest plot

GenderData$AuthorYear = paste(GenderData$Author, GenderData$Year, sep = ", ")

#get the number of male and female ORs
maleNum <- nrow(subset(GenderData, GenderData$Gender=="Male"))
femaleNum <- nrow(subset(GenderData, GenderData$Gender=="Female"))
GenderData$Sample <- ifelse(GenderData$Gender=="Female",GenderData$N_Total_Female,GenderData$N_Total_Male)

# fit random-effects model
res <- rma(yi=OR, sei=se, data=GenderData, slab = paste(Author, Year, sep=", "))
### fit random-effects model in the three subgroups
res.male <- rma(yi=OR, sei=se, data=GenderData[GenderData$Gender == "Male", ])
res.male 
res.female <- rma(yi=OR, sei=se, data=GenderData[GenderData$Gender == "Female", ])
res.female
res.male$data  <- res.male$data[order(res.male$data$Year, res.male$data$Author), ]
res.female$data<- res.male$data[order(res.male$data$Year, res.male$data$Author), ]


compute_prediction_interval <- function(res, df, alpha = 0.05) {
  lower_bound <- exp(res$b - qt(p = alpha / 2, df = df-1, lower.tail = FALSE) * sqrt((res$se)^2 + res$tau2))
  upper_bound <- exp(res$b + qt(p = alpha / 2, df = df-1, lower.tail = FALSE) * sqrt((res$se)^2 + res$tau2))
  return(c(lower_bound, upper_bound))
}
pred_interval_male <- compute_prediction_interval(res.male, df = 6)

pred_interval_female <- compute_prediction_interval(res.female, df = 3)  



result_prediction_interval <- data.frame(
  Study_Type = c("PA for male","PA for female"),
  Lower_Bound = c(pred_interval_male[1], pred_interval_female[1]),
  Upper_Bound = c(pred_interval_male[2],pred_interval_female[2])
)

result_prediction_interval
# a little helper function to add Q-test, I^2, and tau^2 estimate info

print(result_prediction_interval)

```

#---leave 1 out analysis in PA
```{r}
df_male <- leave1out(res.male)
min_row <- df_male[df_male$estimate == min(df_male$estimate), ]
min_ci_lb <- exp(min_row$ci.lb)
min_ci_ub <- exp(min_row$ci.ub)
cat("The minium of OR for male is",exp(min(df_male$estimate)),":", min_ci_lb, "-", min_ci_ub)

max_row <- df_male[df_male$estimate == max(df_male$estimate), ]
max_ci_lb <- exp(max_row$ci.lb)
max_ci_ub <- exp(max_row$ci.ub)
cat("The maximum of OR for male  is",max(exp(df_male$estimate)),":", max_ci_lb, "-", max_ci_ub)

df_female <- leave1out(res.female)
min_row <- df_female[df_female$estimate == min(df_female$estimate), ]
min_ci_lb <- exp(min_row$ci.lb)
min_ci_ub <- exp(min_row$ci.ub)
cat("The minium of OR for female  is",exp(min(df_female$estimate)),":", min_ci_lb, "-", min_ci_ub)

max_row <- df_female[df_female$estimate == max(df_female$estimate), ]
max_ci_lb <- exp(max_row$ci.lb)
max_ci_ub <- exp(max_row$ci.ub)
cat("The maximum of OR for female  is",exp(max(df_female$estimate)),":", max_ci_lb, "-", max_ci_ub)
```


#---forest plot of PA
```{r}
mlabfun <- function(text, res) {
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=2, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(res$I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")")))}

### set up forest plot (with 2x2 table counts added; the 'rows' argument is
### used to specify in which rows the outcomes will be plotted)
jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/Genderplot_PA.jpg", width =3000, heigh = 2000, res=350)
forest(res, at=log(c(0.05, 0.25, 1, 5, 25, 80)), atransf=exp, xlim=c(-11,8), level=95,ilab=cbind(Sample), ilab.xpos=-4,
       cex=0.70, ylim=c(-1, maleNum+femaleNum+10), 
       order= Gender,
       rows=c(3:(maleNum+2), (maleNum+7):(maleNum+femaleNum+6)), 
       header=c("Author,Year","Odds Ratio [95% CI]"), xlab="Odds Ratio (Log scale)", addfit = FALSE)

abline(h = 0, lty = 1, col = "black", lwd = 1) 
### set font expansion factor (as in forest() above) and use a bold font
op <- par(cex=0.75, font=2)
text(-4, maleNum+femaleNum+9, c("Sample Size"))
 
### switch to bold italic font
par(font=4)
 
### add text for the subgroups
text(-11, c(maleNum+femaleNum+7,maleNum+3), pos=4, 
     c("Female", "Male"))
 
### set par back to the original settings
par(op)
 

### add summary polygons for the three subgroups
addpoly(res.female, row=maleNum+5.5, mlab=mlabfun("RE Model for subgroup", res.female))
addpoly(res.male, row= 1.5, mlab=mlabfun("RE Model for subgroup", res.male))
 
### fit meta-regression model to test for subgroup differences
res.meta <- rma(yi=OR, sei=se, mods = ~ Gender, data=GenderData)
summary(res.meta)
 
### add text for the test of subgroup differences
# Calculate the position below the last row

# Add text for the test of subgroup differences
text(x = -11, y =-1, pos = 4, cex = 0.70, 
     bquote(paste("Test for Subgroup Differences: ",
                   Q[M], " = ", .(formatC(res.meta$QM, digits = 2, format = "f")), 
                   ", df = ", .(res.meta$p - 1),
                   ", p = ", .(formatC(res.meta$QMp, digits = 2, format = "f")))))


dev.off
```




#---funplots in PA
```{r}
# egger test and fail safe N
egger_test_male <- regtest(res.male)
egger_test_male

egger_test_female <- regtest(res.female)
egger_test_female

GenderData_male <-  subset(GenderData,GenderData$Gender =="Male")

fsn(res.male,sei = se, data=GenderData, type = "Orwin", target = 0.1)

GenderData_female <-  subset(GenderData,GenderData$Gender =="Female")

fsn(res.female,sei = se, data=GenderData_female, type = "Orwin", target = 0.1)

jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/data analysis/output/Gender difference/publication bias/female_male_PA.jpg", width = 3000, height = 4000, res = 350)

# Define the layout with two rows and one column
par(mfrow = c(2, 1))

# Plot the funnel plot for the threat dimension
metafor::funnel(res.female, main = "Funnel Plot for PA in Woman")

# Plot the funnel plot for the deprivation dimension
metafor::funnel(res.male, main = "Funnel Plot for PA in Men ")

# Close the jpeg device
dev.off()

```




#---multiple meta-regression
```{r}
Gender_MR <- read.csv("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/GenderData_added.csv")
Gender_MR <- subset(Gender_MR, Gender_MR$Author!= "Gayer-Anderson (SA)") 
# excluded ones without female and male sample size

Gender_MR <- subset(Gender_MR, Gender_MR$Author!= "McGrath et al.")


# with CT or withou CT
CT <- factor(Gender_MR$with.CT)
res.meta_mr1 <- rma(yi=OR, sei=se, mods = ~ CT, data=Gender_MR)
summary(res.meta_mr1)

# adversity type
res.meta_mr2 <- rma(yi=OR, sei=se, mods = ~ adversity.type, data=Gender_MR)
summary(res.meta_mr2)

```

# predication interval
```{r}
compute_prediction_interval <- function(res, df, alpha = 0.05) {
  lower_bound <- exp(res$b - qt(p = alpha / 2, df = df-1, lower.tail = FALSE) * sqrt((res$se)^2 + res$tau2))
  upper_bound <- exp(res$b + qt(p = alpha / 2, df = df-1, lower.tail = FALSE) * sqrt((res$se)^2 + res$tau2))
  return(c(lower_bound, upper_bound))
}


# Case-control study
pred_interval_male <- compute_prediction_interval(res.male, df = 33)
# Cross-sectional study
pred_interval_female <- compute_prediction_interval(res.female, df = 36)  
# Cohort study


result_prediction_interval <- data.frame(
  Study_Type = c("CT for male","CT for female"),
  Lower_Bound = c(pred_interval_male[1], pred_interval_female[1]),
  Upper_Bound = c(pred_interval_male[2],pred_interval_female[2])
)

result_prediction_interval



```



#---articles number---
```{r}
df_num <- read_excel("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Main Analysis/article number.xlsx")

df_num$Author <- df_num$First_Author

GenderData <- read_excel("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Gender difference/subgroup/GenderLogOR_main.xlsx")
GenderData <- subset(GenderData, GenderData$Author!= "Millman et al.") #Exclude

combined_df <- merge(GenderData,df_num,by = c("Author", "Year"), all.x = FALSE)
cat("Female")
numbers_female <- combined_df[combined_df$Gender == "Female", "Number"]
sorted_numbers <- sort(numbers_female)
print(paste(sorted_numbers, collapse = ", "))


cat("Male") 
print(paste(combined_df[combined_df$Gender == "Male",]$Number, collapse = ", "))


  rows_not_in_combined <- anti_join(GenderData, combined_df, by = c("Author", "Year"))

# View the rows that are not in combined_df
print(subset(rows_not_in_combined, Gender == "Female"))

print(subset(rows_not_in_combined, Gender == "Male"))  
```



