---
title: "Subgroup Analysis"
author: "Pengyuan Yang"
date: "2023-05-25"
output: html_document
---




```{r}
library(readxl)
library(writexl)
library(metafor)
library(dplyr)
```

# read data--
```{r}
SubData <- read_xlsx("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Preprocessed/LogORData_all_0205.xlsx")
df_num <- read_excel("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Main Analysis/article number.xlsx")

#SubData <- merge(SubData,df_num,by = c("First_Author", "Year"), all.x = FALSE)
#non_duplicates_df1 <- anti_join(df_num,SubData, by = c("First_Author", "Year"))

# Print or explore the non-duplicates
#print(non_duplicates_df1)


colnames(SubData)[c(1,2,3,76)] <- c("Author", "Year", "Study","Design")
SubData <- subset(SubData, SubData$Author!= "Dennison et al.") 
SubData <- subset(SubData, !(Author == "Chen et al." & Year == "2022"))
#Exclude outliers

```

#-----Data Preprocess-----#
```{r}

Sublist <- list()

names <- c("PA","EA","EN","SA","PN","BL","PLD","PS","PD","AP","NL","AB","DM")
NRow <- rep(NA,13)
i=1
while (i<=13) {
  Sublist[[i]] <- list()
  df <- SubData[,c(1:32,(36+3*(i-1)):(38+3*(i-1)),75:88)]
  df <- df[complete.cases(df[,33:35]),]
  # Assuming df is your data frame
  # Assuming df is your data frame
  df[, 33:35] <- lapply(df[, 33:35], as.numeric)
  df[,50] <- ((df[,35]-df[,34])/( 1.96*2))^2
  df$Trauma <- rep(names[i],nrow(df))
  colnames(df)[c(33:35,50)] <- c("LogOR","LogOR_LCI","LogOR_UCI","vi")
  NRow[i] <- nrow(df)
  Sublist[[i]] <- df
  i=i+1
}

names(Sublist) <- names
Sublist <- Sublist[-c(9,13)]  # excluded PD and DM
NRow <- NRow[-c(9,13)]

saveRDS(Sublist, "C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/SubData.RData")


library(dplyr)
library(tidyr)

# Combine the list of data frames into a single dataframe
LongDataFrame <- bind_rows(Sublist, .id = "Trauma")

write.csv(LongDataFrame,"C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/longsubdata.csv")
```

#-----Data Analysis-----#
```{r}
SubData <- readRDS("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/SubData.RData")

SubRes <- list()

i=1
while (i<=11) {
  SubRes[[i]] <- list()
  SubRes[[i]] <- rma(yi=LogOR, vi=vi, data=SubData[[i]])
  i=i+1
}

names(SubRes) <- c("PA","EA","EN","SA","PN","BL","PLD","PS","AP","NL","AB")

SubBind <- dplyr::bind_rows(SubData)
#SubBind$Trauma <- factor(SubBind$Trauma, levels = c("AB","NL","PS","PLD","BL","PN","SA","EN","EA","PA","AP"))

traumaDim <- c("AB","NL","PS","PLD","BL","PN","SA","EN","EA","PA","AP")

orderList <- lapply(traumaDim, function(x) subset(SubBind, Trauma==x))
SubBind <- orderList[[1]][order(orderList[[1]]$Year, orderList[[1]]$Author,decreasing = TRUE),]

for (i in 2:length(orderList)){
  SubBind <- rbind(SubBind,
              orderList[[i]][order(orderList[[i]]$Year, orderList[[i]]$Author,decreasing = TRUE),])
}

SubBind$Trauma <- factor(SubBind$Trauma, levels = c("AB","NL","AP","PS","PLD","BL","PN","SA","EN","EA","PA"))

ResBind <- rma(yi=LogOR, vi=vi, data=SubBind, slab=paste(Author, Year, sep=", "))


mlabfun <- function(text, res) {
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=2, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(res$I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")")))}

Trauma <- c("Physical Abuse", "Emotional Abuse", "Emotional Neglect", "Sexual Abuse", "Physical Neglect", "Bullying", "Parental Loss/Divorce", "Parental Separation","Antipathy", "Neglect", "Abuse")

#Plot
jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/ForestplotSub_0305.jpg", width =3000, heigh = 25000, res=300)

# sum(NRow = max +6)
forest(ResBind, at=log(c(0.25, 1, 4, 40)), atransf=exp, xlim=c(-11,8), level=95,
       cex=0.7, efac=c(0.1,0.1),ylim=c(2, sum(NRow)+46), 
       order=Trauma, 
       rows=c(3:(NRow[11]+2), (NRow[11]+7):(NRow[11]+NRow[10]+6), (NRow[11]+NRow[10]+11):(NRow[11]+NRow[10]+NRow[9]+10),
              (NRow[11]+NRow[10]+NRow[9]+15):(NRow[11]+NRow[10]+NRow[9]+NRow[8]+14), (NRow[11]+NRow[10]+NRow[9]+NRow[8]+19):(NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+18),
              (NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+23):(NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+22), 
              (NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+27):(NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+26), 
              (NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+31):(NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+30),
              (NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+35):(NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+NRow[3]+34),
              (NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+NRow[3]+39):(NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+NRow[3]+NRow[2]+38), (NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+NRow[3]+NRow[2]+43):(NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+NRow[3]+NRow[2]+NRow[1]+42)),header=c("Author,Year","Odds Ratio [95% CI]"), xlab="Odds Ratio (Log scale)", addfit=FALSE,new.page=TRUE)

### switch to bold italic font
op <- par(cex=0.75, font=2)
par(font=4)
 
### add text for the subgroups
text(-11, c(NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+NRow[3]+NRow[2]+NRow[1]+43,NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+NRow[3]+NRow[2]+39,NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+NRow[3]+35,NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+31,NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+27,NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+23,NRow[11]+NRow[10]+NRow[9]+NRow[8]+NRow[7]+19,NRow[11]+NRow[10]+NRow[9]+NRow[8]+15,NRow[11]+NRow[10]+NRow[9]+11,NRow[11]+NRow[10]+7,NRow[11]+3), pos=4, 
     c("Physical Abuse", "Emotional Abuse", "Emotional Neglect", "Sexual Abuse", "Physical Neglect", "Bullying", "Parental Death", "Parental Separation","Antipathy", "Neglect","Abuse"))

### set par back to the original settings
par(op)
 
### fit random-effects model in the three subgroups
 
### add summary polygons for the three subgroups
addpoly(SubRes[[1]], row=NRow[11] + NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+NRow[3]+NRow[2]+41.5, mlab= mlabfun("RE Model for subgroup", SubRes[[1]]))
addpoly(SubRes[[2]], row=NRow[11] + NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+NRow[3]+37.5, mlab= mlabfun("RE Model for subgroup", SubRes[[2]]))
addpoly(SubRes[[3]], row=NRow[11] + NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+NRow[4]+33.5, mlab= mlabfun("RE Model for subgroup", SubRes[[3]]))
addpoly(SubRes[[4]], row= NRow[11] +NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+NRow[5]+29.5, mlab= mlabfun("RE Model for subgroup", SubRes[[4]]))
addpoly(SubRes[[5]], row= NRow[11] +NRow[10]+NRow[9]+NRow[8]+NRow[7]+NRow[6]+25.5, mlab= mlabfun("RE Model for subgroup", SubRes[[5]]))
addpoly(SubRes[[6]], row= NRow[11] +NRow[10]+NRow[9]+NRow[8]+NRow[7]+21.5, mlab= mlabfun("RE Model for subgroup", SubRes[[6]]))
addpoly(SubRes[[7]], row= NRow[11] +NRow[10]+NRow[9]+NRow[8]+17.5, mlab= mlabfun("RE Model for subgroup", SubRes[[7]]))
addpoly(SubRes[[8]], row= NRow[11] +NRow[10]+NRow[9]+13.5, mlab= mlabfun("RE Model for subgroup", SubRes[[8]]))
addpoly(SubRes[[9]], row= NRow[11] + NRow[10]+9.5, mlab= mlabfun("RE Model for subgroup", SubRes[[9]]))
addpoly(SubRes[[10]], row= NRow[11]+5.5, mlab= mlabfun("RE Model for subgroup", SubRes[[10]]))

addpoly(SubRes[[11]], row= 1.5, mlab= mlabfun("RE Model for subgroup", SubRes[[11]]))

dev.off


#Print results
Trauma <- c("Physical Abuse", "Emotional Abuse", "Emotional Neglect", "Sexual Abuse", "Physical Neglect", "Bullying", "Parental Loss/Divorce", "Parental Separation","Antipathy", "Neglect", "Abuse")
OR <- rep(NA,11)
OR_LCI <- rep(NA,11)
OR_UCI <- rep(NA,11)

i=1
while (i<=11) {
  OR[i] <- round(exp(SubRes[[i]][[1]]), digits = 2)
  OR_LCI[i] <- round(exp(SubRes[[i]][[6]]), digits = 2)
  OR_UCI[i] <- round(exp(SubRes[[i]][[7]]), digits = 2)
  i=i+1
}

SubResDf <- data.frame(Trauma, OR, OR_LCI, OR_UCI)
```
#--- model summary
```{r}
# Create a list to store model summaries
SubRes <- list()

i <- 1
while (i <= 11) {
  # Assuming LogOR and vi are columns in SubData[[i]]
  SubRes[[i]] <- rma(yi = SubData[[i]]$LogOR, vi = SubData[[i]]$vi)
  i <- i + 1
}

# Assign names to the list
names(SubRes) <- c("PA","EA","EN","SA","PN","BL","PLD","PS","AP","NL","AB")

# Create an empty data frame to store results
result_df <- data.frame(
  Model = character(length(SubRes)),
  k = numeric(length(SubRes)),
  OR = numeric(length(SubRes)),
  ci_lb = numeric(length(SubRes)),
  ci_ub = numeric(length(SubRes)),
  pval = numeric(length(SubRes)),
  I2 = numeric(length(SubRes)),
  Q = numeric(length(SubRes)),
  Qp = numeric(length(SubRes))
)

# Fill in the data frame with results
for (i in seq_along(SubRes)) {
  result_df[i, "Model"] <- names(SubRes)[i]
  result_df[i, "k"] <- SubRes[[i]]$k
  result_df[i, "OR"] <- exp(SubRes[[i]]$beta)
  result_df[i, "ci_lb"] <- exp(SubRes[[i]]$ci.lb)
  result_df[i, "ci_ub"] <- exp(SubRes[[i]]$ci.ub)
  result_df[i, "pval"] <- SubRes[[i]]$pval
  result_df[i, "I2"] <- SubRes[[i]]$I2
  result_df[i, "Q"] <- SubRes[[i]]$QE
  result_df[i, "Qp"] <- SubRes[[i]]$QEp
}

# Print the resulting data frame
print(result_df)


```
#---prediction interval---
```{r}
# Create a list to store model summaries
SubRes <- list()

i <- 1
while (i <= 11) {
  # Assuming LogOR and vi are columns in SubData[[i]]
  SubRes[[i]] <- rma(yi = SubData[[i]]$LogOR, vi = SubData[[i]]$vi)
  i <- i + 1
}

# Function to compute prediction intervals
compute_prediction_interval <- function(res, df, alpha = 0.05) {
  lower_bound <- exp(res$b - qt(p = alpha / 2, df = df - 1, lower.tail = FALSE) * sqrt((res$se)^2 + res$tau2))
  upper_bound <- exp(res$b + qt(p = alpha / 2, df = df - 1, lower.tail = FALSE) * sqrt((res$se)^2 + res$tau2))
  return(c(lower_bound, upper_bound))
}

# Assign names to the list
names(SubRes) <- c("PA", "EA", "EN", "SA", "PN", "BL", "PLD", "PS", "AP", "NL", "AB")

# Create an empty data frame to store results
result_df <- data.frame(
  Model = character(length(SubRes)),
  PI_lb = numeric(length(SubRes)),
  PI_ub = numeric(length(SubRes)),
  stringsAsFactors = FALSE
)

# Calculate prediction intervals for each model
for (i in seq_along(SubRes)) {
  result_df$Model[i] <- names(SubRes)[i]
  pi_bounds <- compute_prediction_interval(SubRes[[i]], df = SubRes[[i]]$k)
  result_df$PI_lb[i] <- pi_bounds[1]
  result_df$PI_ub[i] <- pi_bounds[2]
}

# Print the resulting data frame
print(result_df)




```


#---leave 1 out analyses
```{r}
# Initialize a list to store results
SubRes <- list()

# Loop through each dataset and calculate the pooled OR and CI
for (i in 1:11) {
  SubRes[[i]] <- rma(yi = SubData[[i]]$LogOR, vi = SubData[[i]]$vi)
}

# Assign names to the list
names(SubRes) <- c("PA", "EA", "EN", "SA", "PN", "BL", "PLD", "PS", "AP", "NL", "AB")

# Create an empty data frame to store results
result_df <- data.frame(
  Model = character(length(SubRes)),
  min_OR = numeric(length(SubRes)),
  min_ci_lb = numeric(length(SubRes)),
  min_ci_ub = numeric(length(SubRes)),
  max_OR = numeric(length(SubRes)),
  max_ci_lb = numeric(length(SubRes)),
  max_ci_ub = numeric(length(SubRes))
)

# Fill in the data frame with results
for (i in seq_along(SubRes)) {
  result_df[i, "Model"] <- names(SubRes)[i]
  result_df[i, "min_OR"] <- exp(SubRes[[i]]$estimate[which.min(SubRes[[i]]$estimate)])
  result_df[i, "min_ci_lb"] <- exp(SubRes[[i]]$ci.lb[which.min(SubRes[[i]]$estimate)])
  result_df[i, "min_ci_ub"] <- exp(SubRes[[i]]$ci.ub[which.min(SubRes[[i]]$estimate)])
  result_df[i, "max_OR"] <- exp(SubRes[[i]]$estimate[which.max(SubRes[[i]]$estimate)])
  result_df[i, "max_ci_lb"] <- exp(SubRes[[i]]$ci.lb[which.max(SubRes[[i]]$estimate)])
  result_df[i, "max_ci_ub"] <- exp(SubRes[[i]]$ci.ub[which.max(SubRes[[i]]$estimate)])
}

# Print the resulting data frame
print(result_df)

```


#---charateristics--
```{r}
# get the sample size for each study

result_sample <- SubBind %>%
  group_by(Trauma) %>%
  summarize(Sum_Sample_Size = sum(Sample.Size_included..N.., na.rm = TRUE))

# Display the result
print(result_sample)


```

---meta regression as male percentages
```{r}
# Create a list to store Egger's test results
SubData <- readRDS("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/SubData.RData")
i <- 1
while (i <= 11) {
  # Assuming LogOR and vi are columns in SubData[[i]]
  SubData[[i]]$Male_ratio <- as.numeric(SubData[[i]]$Male_ratio)
  model <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[[i]])
  
  i <- i + 1
}


mr_SA <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["SA"]])

summary(mr_SA)

mr_PA <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["PA"]])

summary(mr_PA)

mr_EA <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["EA"]])

summary(mr_EA)

mr_AB <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["AB"]])
summary(mr_AB)

mr_PN <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["PN"]])

summary(mr_PN)

mr_EN <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["EN"]])
summary(mr_EN)

mr_NL <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["NL"]])
summary(mr_NL)

mr_BL <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["BL"]])
summary(mr_BL)

mr_PLD <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["PLD"]])
summary(mr_PLD)

mr_PS <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["PS"]])
summary(mr_PS)

mr_AP <- rma(yi = LogOR, vi = vi, mods = ~ Male_ratio, data = SubData[["AP"]])
summary(mr_AP)



```




#---Egger test for publication bias
```{r}
# Create a list to store Egger's test results
EggerResults <- list()

i <- 1
while (i <= 11) {
  # Assuming LogOR and vi are columns in SubData[[i]]
  model <- rma(yi = SubData[[i]]$LogOR, vi = SubData[[i]]$vi)
  
  # Perform Egger's test
  egger_test <- regtest(model)
  
  # Store the Egger's test results in the list
  EggerResults[[i]] <- egger_test
  
  i <- i + 1
}

# Assign names to the list
names(EggerResults) <- c("PA", "EA", "EN", "SA", "PN", "BL", "PLD", "PS","AP", "NL", "AB")

# Print Egger's test results
for (name in names(EggerResults)) {
  cat("Egger's Test for Model", name, ":\n")
  print(EggerResults[[name]])
  cat("\n")
}

```
# ---Orwin's Fail-Safe N
```{r}

OrwinResults <- list()

i <- 1
while (i <= 11) {
  
  # Calculate Orwin's Fail-Safe N using fsn() with specified arguments
  failsafe_N <- fsn(yi = SubData[[i]]$LogOR, vi = SubData[[i]]$vi, data = SubData[[i]], type = "Orwin", target = 0.1)
  
  # Store the results in the list
  OrwinResults[[i]] <- failsafe_N$fsn
  
  i <- i + 1
}

# Assign names to the list
names(OrwinResults) <- c("PA", "EA", "EN", "SA", "PN", "BL", "PLD", "PS","AP", "NL", "AB")

# Print Orwin's Fail-Safe N
for (name in names(OrwinResults)) {
  cat("Orwin's Fail-Safe N for Model", name, ":\n")
  print(OrwinResults[[name]])
  cat("\n")
}


```

#--funnel plot for each subtypes--
```{r}
SubData <- readRDS("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/SubData.RData")

i <- 1
while (i <= 11) {
  # Assign dynamic names to the list based on the index i
  name <- c("PA", "EA", "EN", "SA", "PN", "BL", "PLD", "PS", "AP", "NL", "AB")[i]
  # Save the funnel plot with a dynamic name
  jpeg(paste0("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/publication bias/FunnelPlot_", name, ".jpg"), width = 3000, height = 2000, res = 350)
  
  # Assuming LogOR and vi are columns in SubData[[i]]
  model <- rma(yi = SubData[[i]]$LogOR, vi = SubData[[i]]$vi)
  
  # Plot the funnel plot
  metafor::funnel(model,main = paste("Funnel Plot for", name))
  

  dev.off()
  
  i <- i + 1
}







```







#--excluding poor quality studies
```{r}
# 
SubData <- readRDS("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/SubData.RData")
SubData$SA <- subset(SubData$SA, !(Author == "Friedman & Harrison"))
Res.SA <- rma(yi = SubData$SA$LogOR, vi = SubData$SA$vi)

Res.SA

cat("sexual abuse after excluding one article", exp(Res.SA$beta), ":95%CI [",exp(Res.SA$ci.lb),",",exp(Res.SA$ci.ub),"]")

SubData$PLD <- subset(SubData$PLD, !(Author == "Styla et al."))
Res.PLD <- rma(yi = SubData$PLD$LogOR, vi = SubData$PLD$vi)

Res.PLD

cat("Parental death after excluding one article", exp(Res.PLD$beta), ":95%CI [",exp(Res.PLD$ci.lb),",",exp(Res.PLD$ci.ub),"]")
 
 
```








#---Dimensional approach---
```{r}

longsubdata <- read.csv("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/longsubdata.csv")
df_num <- read_excel("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Main Analysis/article number.xlsx")
df_num$Author <- df_num$First_Author
longsubdata<- merge(longsubdata,df_num,by = c("Author", "Year"), all.x = FALSE)
# exclude the subtypes, parental separation, parental death, parental antipathy, discrimination

longsubdata <- longsubdata %>%
  filter(!Trauma %in% c("DM", "PLD","PS","AP"))


longsubdata <- escalc(measure="OR", yi=LogOR, vi=vi, data=longsubdata, slab=paste("Study", Number))

longsubdata <- longsubdata %>%
  mutate(threat = ifelse(Trauma %in% c("PA", "EA", "BL", "SA", "AB"), 1, 0))

longsubdata <- longsubdata %>%
  mutate(deprivation = ifelse(Trauma %in% c("NL", "PN", "EN"), 1, 0))

longsubdata$threat <- factor(longsubdata$threat)
longsubdata$deprivation <- factor(longsubdata$deprivation)

longsubdata$LogOR <- as.numeric(longsubdata$LogOR)
longsubdata$vi <- as.numeric(longsubdata$vi)

```

##---1. threat and forest plot
```{r}
threat <- longsubdata[longsubdata$threat==1,]
# delete the samples with mutiple articles
exclude_values <- c("95a","130b", "144a", "144b", "179a", "180a", "185b")

threat <- subset(threat, !(Number %in% exclude_values))

## sort the author year
threat <-  threat[order(threat$Year, threat$Author,decreasing = TRUE),]
threat$Trauma <- factor(threat$Trauma)


res1 <- rma.mv(yi=LogOR, vi, data=threat, random = ~ 1 |Number/Trauma, slab=paste(Author, Year, sep=", "))
summary(res1)

#Aggregate studies to the study level
agg <- rma.mv(yi=LogOR, V=vcov(res1, type="obs"), mods = ~ 0 + factor(Number), data=threat, slab=paste(Author, Year, sep=", "))

threat1 <- threat %>%
     distinct(Study, .keep_all = TRUE)
threat1$yi <- coef(agg)

res.th <- rma.mv(yi, V=vcov(agg), method="EE", data = threat1, slab=paste(Author, Year, sep=", "))
summary(res.th)


cat("Threat", exp(res.th$beta), ":95%CI [",exp(res.th$ci.lb),",",exp(res.th$ci.ub),"]")

library(gtools)
threat1$Number <- factor(threat1$Number, levels = mixedsort(unique(threat1$Number)))
threat1 <- threat1[order(threat1$Number), ]
cat(paste(threat1$Number, collapse = ", "), "\n")

write.csv(threat1, "C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/threat_agg.csv")

compute_prediction_interval <- function(res, df, alpha = 0.05) {
  lower_bound <- exp(res$b - qt(p = alpha / 2, df = df - 1, lower.tail = FALSE) * sqrt((res$se)^2 + res$sigma2[1]))
  upper_bound <- exp(res$b + qt(p = alpha / 2, df = df - 1, lower.tail = FALSE) * sqrt((res$se)^2 + res$sigma2[1]))
  return(c(lower_bound, upper_bound))
}
cat(" the smaple size of Threat:",sum(threat1$Sample.Size_included..N.., na.rm = TRUE))
# sample size
cat(" 95% PI of Threat is:",compute_prediction_interval(res1, 306, alpha = 0.05))

# publicatio bias
set.seed(123)
cat(" fail safe N for threat is:")
fsn(yi, vi, data=threat1, type = "Orwin", target= 0.1)

egg_th <- rma.mv(yi ~ 1 + sqrt(vi), vi, random = ~ 1 | Study/Trauma, data = threat, test = "t")
summary(egg_th)
```
#--leave 1 out analysis
```{r}
leave_one_out_analysis <- function(data, outcome, variance, Number) {
  Number <- unique(data[[Number]])
  num_studies <- length(Number)
  
  # Initialize matrices to store results
  results <- matrix(NA, nrow = num_studies, ncol = 6, 
                    dimnames = list(NULL, c("Study_ID", "Pooled_OR", "ci.lb", "ci_ub")))
  
  for (i in 1:num_studies) {
    # Subset the data to leave out the i-th study
    subset_data <- data[data[[Number]] != Number[i], ]
    
    # Fit the meta-analysis model without the i-th study
    model <- rma.mv(yi = subset_data[[outcome]], V = subset_data[[variance]], 
                    data = subset_data, random = ~ 1 |Number/Trauma,
                    slab = paste(subset_data$Author, subset_data$Year, sep = ", "))
    
    # Obtain the pooled effect size
    res <- summary(model)
    pooled_effect <- coef(model)
    ci_lb <- res$ci.lb
    ci_ub <- res$ci.ub
    p_value <- res$pval
    
    # Store the pooled effect size
    results[i, ] <- c(study_ids[i], exp(pooled_effect), exp(ci_lb), exp(ci_ub))
  }
  return(results)
}
results <- leave_one_out_analysis(threat, LogOR, vi, Number)

```



##--2. deprivation and and forest plot
```{r}
deprivation <- longsubdata[longsubdata$deprivation==1,]

res2 <- rma.mv(yi=LogOR, vi, data=deprivation, random = ~ 1 |Study/Trauma, slab=paste(Author, Year, sep=", "))
summary(res2)

#Aggregate studies to the study level
agg_dp <- rma.mv(yi=LogOR, V=vcov(res2, type="obs"), mods = ~ 0 + factor(Number), data=deprivation, slab=paste(Author, Year, sep=", "))

deprivation1 <- deprivation %>%
     distinct(Study, .keep_all = TRUE)
deprivation1$yi <- coef(agg_dp)

res.dp <- rma.mv(yi, V=vcov(agg_dp), method="EE", data = deprivation1, slab=paste(Author, Year, sep=", "))
summary(res.dp)

write.csv(deprivation1, "C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/deprivation_agg.csv")

cat("Deprivation", exp(res.dp$beta), ":95%CI [",exp(res.dp$ci.lb),",",exp(res.dp$ci.ub),"]")

deprivation1$Number <- factor(deprivation1$Number, levels = mixedsort(unique(deprivation1$Number)))
deprivation1 <- deprivation1[order(deprivation1$Number), ]
cat(paste(deprivation1$Number, collapse = ", "), "\n")

cat(" the smaple size of deprivation:",sum(deprivation1$Sample.Size_included..N.., na.rm = TRUE))

cat(" prediction intervals:",compute_prediction_interval(res2, 139, alpha = 0.05))

# publicatio bias
set.seed(123)
cat(" fail safe N for deprivation is:")
fsn(yi, vi, data=deprivation1, type = "Orwin", target= 0.1)

egg_dp <- rma.mv(yi ~ 1 + sqrt(vi), vi, random = ~ 1 | Study/Trauma, data = deprivation, test = "t")
summary(egg_dp)
```
#--forest plot
```{r}
thNum <- nrow(threat1)
dpNum <- nrow(deprivation1)

### a little helper function to add Q-test, I^2, and tau^2 estimate info
mlabfun <- function(text, res, levels) {
   W <- diag(1/res$vi)
   X <- model.matrix(res)
   P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
   I2 <- 100 * res$sigma2[levels-1] / (sum(res$sigma2) + (res$k-res$p)/sum(diag(P)))
  
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=3, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$sigma2[levels-1], digits=2, format="f")), ")")))}


jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/Forestplot_threat1.jpg", width =3000, heigh = 8000, res=300)
forest(res.th, at=log(c(0.25, 1, 4, 40)), xlim=c(-11,8), level=95, atransf = exp,
     
       cex=0.7, efac=c(0.4,0.4), 
       order= Year, 
       header=c("Author,Year","Odds Ratio [95% CI]"), xlab="Odds Ratio (Log scale)", mlab = mlabfun("Multilevel Model for All Studies", res1, 2))
### set font expansion factor (as in forest() above) and use a bold font
op <- par(cex=0.75, font=2)
dev.off



jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/Forestplot_deprivation1.jpg", width =3000, heigh = 5000, res=300)
forest(res.dp, at=log(c(0.25, 1, 4, 40)), xlim=c(-11,8), level=95, atransf = exp,
     
       cex=0.7, efac=c(0.4,0.4), 
       order= Year, 
       header=c("Author,Year","Odds Ratio [95% CI]"), xlab="Odds Ratio (Log scale)", mlab = mlabfun("Multilevel Model for All Studies", res2, 2))
### set font expansion factor (as in forest() above) and use a bold font
op <- par(cex=0.75, font=2)
dev.off
```



# test the difference between threat and deprivation
```{r}
com_df <- rbind(threat,deprivation)
# Assuming com_df is your data frame
com_df$Dimension <- ifelse(com_df$deprivation == 1, 1, 0)
# Assuming com_df is your data frame
com_df$Study_num <- ifelse(com_df$Dimension == 1, paste0(com_df$Number, "d"), paste0(com_df$Number, "t"))


reg.dif <- rma.mv(yi=LogOR, vi, data=com_df, random = ~ 1 |Study_num/Number/Trauma, mods = ~factor(Dimension))
summary(reg.dif)

```

#--Publication bias for the dimensional analyses

```{r}
#Egger's regression

# Egger Test for threat
res1_egg_mod_se <- rma.mv(yi~ 1 + sqrt(vi), vi, data=threat, random = ~ 1 |Number/Trauma,test = "t")
summary(res1_egg_mod_se)

# Egger Test for deprivation
res2_egg_mod_se <- rma.mv(yi~ 1 + sqrt(vi), vi, data=deprivation, random = ~ 1 |Number/Trauma,test = "t")
summary(res2_egg_mod_se)

```

```{r}
jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/publication bias/FunnelPlot_threat_and_deprivation.jpg", width = 3000, height = 4000, res = 350)

# Define the layout with two rows and one column
par(mfrow = c(2, 1))

# Plot the funnel plot for the threat dimension
metafor::funnel(res.th, main = "Funnel Plot for Threat Dimension")

# Plot the funnel plot for the deprivation dimension
metafor::funnel(res.dp, main = "Funnel Plot for Deprivation Dimension")

# Close the jpeg device
dev.off()

```
# sensitivity analysis with Rho in threat

```{r}
rho.sens <- seq(0, 0.7, 0.1) # determine a set of rhos
model.sens <- lapply(rho.sens, 
                     function(x) 
                       {V <- vcalc(vi, cluster=Number, obs=Trauma, 
                                   data=threat, rho = x)
                        res.rho <- rma.mv(yi=LogOR, V, 
                                          data=threat, 
                                          random = ~ 1 |Number/Trauma,
                                          slab=paste(Author, Year, sep=", "))}) 

# Prediction intervals
Pred_int <- function(mod, lvl){
  SE <- mod$se
  tau2 <- mod$sigma2[lvl]
  df <- mod$k - mod$p
  result <- c(LCI=exp(mod$b - qt(0.975, df-1)*sqrt(SE^2+tau2)),
              UCI=exp(mod$b + qt(0.975, df-1)*sqrt(SE^2+tau2)))
  result
}

df_PI <- t(vapply(model.sens, function(mod) Pred_int(mod,1), numeric(2)))

# Heterogeneity
I2 <- function(res.rho){
  W <- diag(1/res.rho$vi)
  X <- model.matrix(res.rho)
  P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W

  100*res.rho$sigma2/(sum(res.rho$sigma2)+(res.rho$k-res.rho$p)/sum(diag(P)))
}

pooled.sens <- vapply(model.sens, function(mod) exp(mod$b), numeric(1))
CIs.sens <- vapply(model.sens, function(mod) c(exp(mod$ci.lb),exp(mod$ci.ub)), numeric(2))


# Result_overall
result_overall <- data.frame(rho.sens, pooled.sens, CIs.sens,df_PI)


jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/sensitivity analysis/roh_threat.jpg", width = 3000, height = 2000,res = 350)
ggplot(result_overall,
       aes(x = rho.sens,
           y = pooled.sens)) +
  geom_point() +
  geom_line() +
  geom_errorbar(mapping = aes(ymax = CIs.sens[2, ], ymin = CIs.sens[1, ]), width = 0.02, color = "blue") +
  geom_errorbar(mapping = aes(ymax=UCI, ymin=LCI), width = 0.02, color = "green") +
  geom_hline(yintercept = 1, color = "red", linetype = "dashed") +
  ylim(c(0, 10)) +
  scale_y_continuous(breaks = seq(0, 10, 1)) +
  scale_x_continuous(breaks = seq(0, 0.95, 0.05)) +
  labs(x = "Rho", y = "Pooled Odds Ratios", color = "Error Bars")+
  scale_color_manual(values = c("CI" = "blue", "PI" = "green"),
                     labels = c("95% Confidence Intervals", "95% Prediction Intervals"),
                     name = "Intervals") + # Provide a name for the legend
  theme(legend.position = "bottom") + # Move legend to the bottom
  guides(color = guide_legend(override.aes = list(linetype = c("solid", "dashed")))) # Adjust linetype in legend

dev.off()


```

# sensitivity analysis with Rho in deprivation
```{r}
rho.sens <- seq(0, 0.7, 0.1) # determine a set of rhos
model.sens <- lapply(rho.sens, 
                     function(x) 
                       {V <- vcalc(vi, cluster=Number, obs=Trauma, 
                                   data=deprivation, rho = x)
                        res.rho <- rma.mv(yi=LogOR, V, 
                                          data=deprivation, 
                                          random = ~ 1 |Number/Trauma,
                                          slab=paste(Author, Year, sep=", "))}) 

# Prediction intervals
Pred_int <- function(mod, lvl){
  SE <- mod$se
  tau2 <- mod$sigma2[lvl]
  df <- mod$k - mod$p
  result <- c(LCI=exp(mod$b - qt(0.975, df-1)*sqrt(SE^2+tau2)),
              UCI=exp(mod$b + qt(0.975, df-1)*sqrt(SE^2+tau2)))
  result
}

df_PI <- t(vapply(model.sens, function(mod) Pred_int(mod,1), numeric(2)))

# Heterogeneity
I2 <- function(res.rho){
  W <- diag(1/res.rho$vi)
  X <- model.matrix(res.rho)
  P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W

  100*res.rho$sigma2/(sum(res.rho$sigma2)+(res.rho$k-res.rho$p)/sum(diag(P)))
}

pooled.sens <- vapply(model.sens, function(mod) exp(mod$b), numeric(1))
CIs.sens <- vapply(model.sens, function(mod) c(exp(mod$ci.lb),exp(mod$ci.ub)), numeric(2))


# Result_overall
result_overall <- data.frame(rho.sens, pooled.sens, CIs.sens,df_PI)


jpeg("C:/Users/Lauren/Desktop/meta analysis/data analysis/output/Sub Analysis/sensitivity analysis/roh_deprivation.jpg", width = 3000, height = 2000,res = 350)
ggplot(result_overall,
       aes(x = rho.sens,
           y = pooled.sens)) +
  geom_point() +
  geom_line() +
  geom_errorbar(mapping = aes(ymax = CIs.sens[2, ], ymin = CIs.sens[1, ]), width = 0.02, color = "blue") +
  geom_errorbar(mapping = aes(ymax=UCI, ymin=LCI), width = 0.02, color = "green") +
  geom_hline(yintercept = 1, color = "red", linetype = "dashed") +
  ylim(c(0, 10)) +
  scale_y_continuous(breaks = seq(0, 10, 1)) +
  scale_x_continuous(breaks = seq(0, 0.95, 0.05)) +
  labs(x = "Rho", y = "Pooled Odds Ratios", color = "Error Bars")+
  scale_color_manual(values = c("CI" = "blue", "PI" = "green"),
                     labels = c("95% Confidence Intervals", "95% Prediction Intervals"),
                     name = "Intervals") + # Provide a name for the legend
  theme(legend.position = "bottom") + # Move legend to the bottom
  guides(color = guide_legend(override.aes = list(linetype = c("solid", "dashed")))) # Adjust linetype in legend

dev.off()


```


